Isomorphisms as Groupoids: \\ Homotopy Type Theory and Fractional Types

### 2013-10-20 f.tex

So generally speaking $\eta_n$ will produce a product of $\br_n$ and $n$ and
$\epsilon_n$ will be the group action of the group on $\br_n$ on the
particular strand $n$.

>>>>

So generally speaking $\eta_n$ will produce a product of $\br_n$ and $n$ and
$\epsilon_n$ will be the group action of the group on $\br_n$ on the
particular strand $n$. A function will have a particular wiring; this wiring
is reflected as a first class value using the group generators. For booleans,
the group generators can be represented as id, not, and not'; every wiring is
a sequence of these. So values of type $1/bool$ are (id), (not o not'), (not'
o not'), (not o not o not), etc. or in other words the code for the circuits
becomes represented as a value. (Is that related to the encode/decode method
in the HoTT book?) How about functions: T1 -> T2. The types T1 and T2 must be
connected by paths so we might as well think about T1 -> T1.

So B has value f and t
1/B has values id; not; not'; and their compositions (semantically
represented as elements of the group Br2.

eta : (1,()) -> ((B,1/B),(f,id))
eta () = (f , id)

eta : (1,()) -> ((B,1/B),(f,not))
eta () = (t , not)

...

epsilon : ((B,1/B),(f,not)) -> (1,())
epsilon (t , not) = ()

...
